---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 17"
author: "Jason Abu"
output: html_notebook
---

## Assigned Exercises

DC Ch 17 Exercises: 17.1, 17.3, 17.4, 17.5, 17.7

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)
library(tidyr)
library(lubridate)
library(ggplot2)
library(dplyr)

```



## Chapter 17 Exercises


### Problem 17.1
the 10 most popular names according to each of these criteria:
Boys’ names ending in a vowel

```{r}
regex <- " .*([aeiou])$"
Boy_names <- BabyNames %>% group_by(name) %>% filter(grepl(pattern = regex,name), sex == "M") %>%
  summarise(s = sum(count)) %>% filter(rank(desc(s)) <= 10)
Boy_names

```
Names with a space (like Lee Ann)
```{r}
BabyNames %>%
  group_by(sex,name)%>%
  filter(grep("\\s", name))%>%
  summarise(total=sum(count))%>%
  arrange(desc(total))%>%
  head(10)

```
Names ending with “joe” (like BettyJoe)
```{r}
BabyNames%>%
  filter(grepl("Joe|joe$", name)) %>%
  group_by(name) %>%
  summarise(total = sum(count)) %>%
  arrange(desc(total))

```

### Problem 17.3
The string would represents a phone number. The digits of that phone number are being extracted


### Problem 17.4
1 The strings would be 2 characters long.

2 It would be the same amount as there are US states and territories.

3 Those are U.S. states abbreviations.

### Problem 17.5
```{r}
BibleNames <- 
  readr::read_csv("http://tiny.cc/dcf/BibleNames.csv")
```
1
```{r}
Names <- BibleNames %>% group_by(name) %>% filter(grepl(pattern = "^Bar|bar...$|bar$|^Dam|dam...$|dam$|^Lory|lory...$|lory$", name))
Names
```
2
```{r}
EndNames <- BibleNames %>% group_by(name) %>% 
  filter(grepl(pattern = "bar$|dam$|lory$", name))
EndNames
```

### Problem 17.7
```{r}
BabyBibleNames <- BibleNames %>% left_join(BabyNames, by = c("name" = "name")) %>%
  group_by(name) %>% summarise(total= sum(count)) %>% filter(rank(desc(total)) <= 10)
BabyBibleNames
```


