---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 10"
author: "Jason Abu"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 10 Exercises 10.1 - 10.7

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)

```



## Chapter 10 Exercises

### Problem 10.1
```{r}
```
Str() - summary function
group_by() - data verb
rank() - data verb
mean() - reduction function
filter()- data verb
summary()- summary function
summarize()- data verb
glimpse()- summary function

### Problem 10.2

```{r}
```
1. mutate()
2. arrange()
3. transmute()
4. transmute()
5.

### Problem 10.3

```{r}
```
1. nrow()
2. names()
3. view()
4. read()
5. 

### Problem 10.4
```{r}
```
For Output Table A - arrange( asc(count))
For Output Table B - 
For Output Table C - name(Yadriel)
For Output Table D - select(total)
For Output Table E - select(name, count)
### Problem 10.5
```{r}
```

### Problem 10.6
```{r}
```

### Problem 10.7
```{r}
```

