---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 12"
author: "Jason Abu"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 8 Exercises 12.1, 12.2, 12.3, 12.4

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)
library(tidyr)

```



## Chapter 12 Exercises

### Problem 12.1

```{r}
view(BabyNames)
```
1. BothSexes replaces ???
```{r}
BothSexes <-
  BabyNames %>%
  spread (key=sex, value= count) %>% 
  filter(F>1, M>1)

BothSexes
```
2.
```{r}
  BothSexes%>%
  group_by(name) %>%
  mutate(genderBalance=abs(log(F/M))) %>%
  arrange(genderBalance)
```
3.
4.
5.

### Problem 12.2
1. Version 1 cases represents the number of babies of each name born in diferent years. Version 2 cases represents both sexes count per year. Version 3 is the count of names in 1912 and 2012.
2. Version 2 is wider. Therefore the code looks like: 
spread (key=sex, value=nbabies)
3. Version 3 is wider. Therefore the code looks like:
gather(key=year, value=count, "1912", "2012")
4.
5.


### Problem 12.3
1.Data Frame A is wider then Data Frame C
Data Frame C is wider then Data Frame B
Data Frame A is wider then Data Frame B
2. Data Frame B. You can find the change by taking the difference between the years.
3. Data Frame A would make it easier to find sum of values.


### Problem 12.4
1. The resulting data frame might be "too narrow" because the subject being one of the variables in the value = section is redundant.
2.BP_wide %>%
  gather(key = when, value = sbp, before, after)


