---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 18"
author: "Jason Abu"
output: html_notebook
---

## Assigned Exercises

DC Ch 17 Exercises: 18.1, 18.2

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)
library(tidyr)
library(lubridate)
library(ggplot2)
library(dplyr)
install.packages("party")

```



## Chapter 18 Exercises


### Problem 18.1
1. The variables are living_area, bathrooms, bedrooms, fireplaces.

2. For houses less than 1080 square feet the number of bathrooms do not make a difference because they are noot bathrooms less than 1080.

3. Difference is typically $28,372.15

4. Having a fireplace is indeed associated with a higher house price, this is also dependent on the living area as well.

### Problem 18.2
```{r}
NCHS %>%
  na.omit() %>%
  nrow()
```

```{r}
CompleteCases <- 
  NCHS %>%
  select(diabetic, weight, age, bmi, chol, smoker) %>%
  na.omit()
```

```{r}
CompleteCases %>% nrow()
```

```{r}
mod1 <- party::ctree(diabetic ~ weight + chol, data = CompleteCases)

plot(mod1, type = "simple")
```

```{r}
CompleteCases %>%
  mutate(probability = as.numeric(predict(mod1)), 
         likelihood = ifelse(diabetic, probability, 1-probability)) %>%
  summarise(log_likelihood = sum(log(likelihood)))
```


```{r}
Case2 <-
  NCHS %>%
  select(diabetic, weight, age, bmi, chol, smoker, ptfat, tfat, lfat) %>%
  na.omit()
Case2 %>% nrow()
mod2 <- party::ctree(diabetic ~ ptfat + tfat, data = Case2)

```

```{r}
mod2 <- party::ctree(diabetic ~ ptfat + tfat, data = Case2)
plot(mod2, type = "simple")
```


```{r}
Case2 %>%
  mutate(probability = as.numeric(predict(mod2)),
         likelihood = ifelse(diabetic, probability, 1-probability)) %>%
  summarise(log_likelihood = sum(log(likelihood)))

```

3. At n = 343 the probability of getting diabetes is at 0.303


4. At n  = 2050 the probability of getting diabetes is 0.001


